---
title: "P8105 Homework 5: Iteration"
author: "Catherine Lucey (cml2270)"
date: "11/11/2021"
output: github_document
---

# Setup
Only done once, the setup code loads the necessary libraries and double checks that the working directory is correct. It also sets defaults for figure size with knitr, as well as a default theme and color scale for all ggplots.

```{r setup}
library(tidyverse)
library(readr)
getwd()

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

# Problem 1: Washington Post Unsolved Homicides Data

#### Installing and Describing the WaPo Homicides Data

DO THE REMOVE WITHIN THE READ CSV CALL

COUNT(VARIABLE NAME)

```{r load data}

urlfile = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

hom_df = 
  read_csv(url(urlfile)) %>% 
   mutate(city_state = str_c(city, ", ", state))
  
```

The homicides dataset contains 53179 observations of 12 variables, these variables include LITERALLY HOW DO YOU DO THIS/???

```{r clean data}

n_homs =
  hom_df %>% 
  group_by(city_state, disposition) %>%
  summarise(n_hom_type = n()) %>% 
  mutate(n_hom_type = as.numeric(n_hom_type)) %>% 
  pivot_wider(names_from = disposition,
              values_from = n_hom_type
  ) %>% 
  mutate(`Closed without arrest` = replace_na(`Closed without arrest`, 0)) %>% 
  mutate(`Open/No arrest` = replace_na(`Open/No arrest`, 0)) %>% 
  mutate(n_total_homs = sum(`Closed by arrest`, `Closed without arrest` , `Open/No arrest`)) %>% 
  mutate(n_unsolved = sum(`Closed without arrest`, `Open/No arrest`)) %>% 
  select(city_state, n_total_homs, n_unsolved) %>%
  filter(city_state != "Tulsa, AL")

```

#### Proportion Unsolved Homicides in Baltimore, MD

```{r}

bmore_unsolved =
  n_homs %>% 
  filter(city_state == "Baltimore, MD")

prop_results = prop.test(x = bmore_unsolved$n_unsolved, n = bmore_unsolved$n_total_homs, alternative = "two.sided", conf.level = 0.95, correct = FALSE) %>% 
  broom::tidy() %>% 
  mutate(conf_int = str_c(round((conf.low*100), 2), ", ", round((conf.high*100), 2))) %>% 
  select(estimate, conf_int)

```

#### Writing a Function to Estimate Proportion Unsolved Murders in All Cities

```{r define fxn}

city_prop_unsolved = function(cityname) {
  city_unsolved =
    n_homs %>% 
    filter(city_state == cityname)
  
  prop_results =
    prop.test(x = city_unsolved %>% pull(n_unsolved), 
              n = city_unsolved %>% pull(n_total_homs), 
              alternative = "two.sided", 
              conf.level = 0.95, 
              correct = FALSE) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high) %>% 
    mutate(city_name = cityname) %>% 
    as.tibble()
  return(prop_results)
}

# test the function!
city_prop_unsolved(cityname = "Atlanta, GA")

```

#### Calculating the Proportion of Unsolved Homicides with CIs for All Cities

```{r}

all_cities_props = map(n_homs$city_state, city_prop_unsolved) %>% 
  bind_rows()

```

#### Plotting Estimated Proportions of Unsolved Homicides in U.S. Cities

```{r plotting homs data}

all_cities_props %>% 
  mutate(city_name = fct_reorder(city_name, estimate)) %>% 
  ggplot(aes(x = city_name, y = estimate)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, 
                    ymax = conf.high))

```

# Problem 2: Trial Data

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

    Start with a dataframe containing all file names; the list.files function will help
    Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
    Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

THIS IS SUPER WRONG 


```{r error = TRUE}

file_names_df =
  tibble(
    file_name = list.files("data")
  )

output_df = map_df(file_names_df, read.csv)

read_trialv6 = function(file_name){
  path = str_c("'", "data/", file_name, "'")
  read.csv(path)
}

output_df = map_df(file_names_df, read_trialv6)

```


```{r error = TRUE}

test1 = read.csv('data/con_01.csv')

read_trial = function(x){
  path = str_c("./data/", x)
}

read_trialv3 = function(file_name){
  path = str_c("'", "data/", file_name, "'")
  read.csv(path)
}

fxn_output = map(file_names_df, read_trialv3)

output_df = map(file_names_df, read_trialv3)

read_trialv3(file_names_df)

read_trialv2 = function(file_name){
  read.csv2(file_name)
}

read_trialv4 = function(path){
  read.csv(path)
  return()
}

read_trialv5 = function(file_name){
  path = paste("data/", file_name,".csv", sep = "")
  read.csv(path)
}

output_df = map(file_names_df, read_trialv5)
  
  
 # output_df = read.csv()




test = read_trial(file_names_df[[1]])

CODE FROM THE INTERNET:
path<-paste(directory,"/", file_name,".csv",sep="")



for (file_name in file_names_df) {
  output_df = 
      read_trialv3(file_name)
}

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}


file_names_df %>% 
  read_trial(x = file_name)

  

read_data = map(file_names_df, read_trial)
  
file_names_df %>% 
  filter(file_name == "con_01.csv") %>%
  mutate(path = str_c("./data/", file_name)) %>% 
  read.csv("path")
```

```{r}

path = str_c("./data/", file_names_df[[1]]) %>% 
  return(path)
```

# Problem 3: Iteratively Fixing Missing Values in Iris Data

#### Loading the Data and Introducing Missing Values

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

#### Fixing the Dataset

There are two cases to address:

    For numeric variables, you should fill in missing values with the mean of non-missing values
    For character variables, you should fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}

add_missing = function(x){
  
  if (is.double(x)) {
    avg = round(mean(x, na.rm = TRUE), digits = 2)
    x = replace_na(x, avg)
    return(x)
  }
  
  if (is.character(x)) {
    x = replace_na(x, "virginica")
    return(x)
  }
}

replaced_df = map_df(iris_with_missing, add_missing)


```
